Solving the Poisson-equation in one dimension \\ \hrulefill\small{ FYS3150: Computational Physics }\hrulefill

### 2016-09-16 Project1/article/article.tex
Discussion

\begin{figure}[h]
  \centering
  \includegraphics[width=0.9\linewidth]{figures/relerror.png}
  \caption{Plot of maximum relative error as a function of step size}
  \label{fig:relerror}
\end{figure}
\section{Discussion}

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=0.9\linewidth]{figures/relerror.png}
  \caption{Plot of maximum relative error as a function of step size}
  \label{fig:relerror}
\end{figure}

\section{Discussion}
When choosing a suitible value for $n$, one must take into account both precision and speed. Our intuition tells us that a larger $n$ should result in a higher precision for the numerical derivative. We can conclude from figure \ref{fig:relerror} that this is only true up to a certain point, because of loss in numerical representation accuracy within the computer. An ideal n will be in the range of $n\approx 10^5$ which is equivalent to $h=10^-5$. Increasing this value will not increase run time dratically for the tridiagnoal matrix algorithm. Choosing $n=10^5$ leaves us with the ability to calculate with a high certainty of 5 decimals points and with low memory cost.

By looking at the results one is led to believe that there are more reasons to prefer the tridiagonal matrix algorithm for this kind of problem. When using the LU-decomposition method the short term memory is quickly filled with nothing but the matrix $A$. Choosing $n=10^5$ is equivalent to $8\times10^{10}$ bytes$=80$GB of memory! A brand new computer ships with around $8$ GB of memory today, which is a tenth of the space required. Obviously, this inhibits our ability to perform the calculation.
